Methodology for Assessing the State of the Practice for Domain X

### 2021-10-20 StateOfPractice/Methodology/Methodology.tex
Updates to sections other than future work and conclusions are mostly done

The Analytical Hierarchy Process (AHP) is a decision-making technique that can
be used when comparing multiple options by multiple criteria. In our work AHP is
used for comparing and ranking the software packages of a domain using the
quality scores that are gathered in the Measurement Template
(Appendix~\ref{SecGradingTemplate}). AHP performs a pairwise analysis between
each of the quality options using a matrix which is used to generate an overall
score for each software package for the given criteria. \cite{SmithEtAl2016}
shows how AHP is applied to ranking software based on quality measures. We have
developed a
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2020/LBM/README.txt}{tool}
for conducting this process. The tool includes an AHP JAR script and a
sensitivity analysis JAR script that is used to ensure that the software package
rankings are appropriate with respect to the uncertainty of the quality scores.
The
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2020/LBM/README.txt}{README
file} outlines the requirements for, and configuration and usage of, the JAR
scripts. The JAR scripts, source code, and required libraries are located in the
same folder as the README file.

@@

The installation steps on your machine may be different from this section.
Please refer to the user manual mentioned in Section \ref{git_stats_manual}, if
necessary.  The steps shown here were executed on a virtual machine with 8 cores
and 16 GB RAM running Debian GNU/Linux 9.11

@@

The table below lists the full set of measures that are assessed for each
software product.  The measures are grouped under headings for each quality, and
one for summary information.  Following each measure, the type for a valid
result is given in brackets.  Many of the types are given as enumerated sets.
For instance, the response on many of the questions is one of ``yes,'' ``no,''
or ``unclear.''  The type ``number'' means natural number, a positive integer.  The
types for date and url are not explicitly defined, but they are what one would
expect from their names.  In some cases the response for a given question is not
necessarily limited to one answer, such as the question on what platforms are
supported by the software product.  Case like this are indicated by ``set of''
preceding the type of an individual answer.  The type in these cases are then
the power set of the individual response type.  In some cases a superscript $^*$
is used to indicate that a response of this type should be accompanied by
explanatory text.  For instance, if problems were caused by uninstall, the
reviewer should note what problems were caused.  An (I) precedes the question
description when its measurement requires a successful installation.

The table below lists the set of measures that are used to assess each software
product. The first set identifies summary information, followed by 9 sets for
software qualities and 3 sets for raw metrics. Each measure is followed by the
type for a valid result. A superscript $^*$ indicate that a response of this type
needs to be accompanied by explanatory text.

@@

$\mathit{ab} \mathit{val}$

@@

>>>>

The Analytical Hierarchy Process (AHP) is a decision-making technique that can
be used when comparing multiple options by multiple criteria. In our work AHP is
used for comparing and ranking the software packages of a domain using the
quality scores that are gathered in the Measurement Template
(Appendix~\ref{SecGradingTemplate}). AHP performs a pairwise analysis between
each of the 9 quality options for each of the 30 software packages.  This
results in a matrix, which is used to generate an overall score for each
software package for the given criteria. \cite{SmithEtAl2016} shows how AHP is
applied to ranking software based on quality measures. We have developed a
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2020/LBM/README.txt}{tool}
for conducting this process. The tool includes an AHP JAR script and a
sensitivity analysis JAR script that is used to ensure that the software package
rankings are appropriate with respect to the uncertainty of the quality scores.
The
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2020/LBM/README.txt}{README
file} outlines the requirements for, and configuration and usage of, the JAR
scripts. The JAR scripts, source code, and required libraries are located in the
same folder as the README file.

@@

The installation steps on your machine may be different from this section.
Please refer to the user manual mentioned in Section \ref{git_stats_manual}, if
necessary.  The steps shown here were executed on a virtual machine with 8 cores
and 16 GB RAM running Debian GNU/Linux 9.11.

@@

The table below lists the full set of measures that are assessed for each
software product.  The measures are grouped under headings for each quality, and
one for summary information.  Following each measure, the type for a valid
result is given in brackets.  Many of the types are given as enumerated sets.
For instance, the response on many of the questions is one of ``yes,'' ``no,''
or ``unclear.''  The type ``number'' means natural number, a positive integer.  The
types for date and url are not explicitly defined, but they are what one would
expect from their names.  In some cases the response for a given question is not
necessarily limited to one answer, such as the question on what platforms are
supported by the software product.  Case like this are indicated by ``set of''
preceding the type of an individual answer.  The type in these cases are then
the power set of the individual response type.  In some cases a superscript $^*$
is used to indicate that a response of this type should be accompanied by
explanatory text.  For instance, if problems were caused by uninstall, the
reviewer should note what problems were caused.  % An (I) precedes the question
% description when its measurement requires a successful installation.
The template also include 3 sections at the end for summarizing the repository
based metrics.  A
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}
{blank measurement template spreadsheet} is available to save time with data
entry.

@@

@@

% \def\arraystretch{1.22}
% \begin{tabular}{p{14cm}}
% \hline
% \textbf{Repo Metrics (Measured via git_stats)}\\
% \hline
% Number of text-based files. (number)\\
% Number of binary files. (number)\\
% Number of total lines in text-based files. (number)\\
% Number of total lines added to text-based files. (number or {not git repo})\\
% Number of total lines deleted from text-based files. (number or {not git repo})\\
% Number of total commits. (number or {not git repo})\\
% Numbers of commits by year in the last 5 years. (Count from as early as possible if the project is younger than 5 years.) (list of numbers or {not git repo}\\
% Numbers of commits by month in the last 12 months. (list of numbers or {not git repo})\\
% \hline
% \end{tabular}

% \def\arraystretch{1.22}
% \begin{tabular}{p{14cm}}
% \hline
% \textbf{Repo Metrics (Measured via scc)}\\
% \hline
% Number of text-based files.	(number)\\
% Number of total lines in text-based files.	(number)\\
% Number of code lines in text-based files.	(number)\\
% Number of comment lines in text-based files.	(number)\\
% Number of blank lines in text-based files.	(number)
% \hline
% \end{tabular}

% \def\arraystretch{1.22}
% \begin{tabular}{p{14cm}}
% \hline
% \textbf{Repo Metrics (Measured via GitHub)}\\
% \hline
% Number of stars.	(number or {n/a})
% Number of forks.	(number or {n/a})
% Number of people watching this repo.	(number or {n/a})
% Number of open pull requests.	(number or {n/a})
% Number of closed pull requests.	(number or {n/a})
% \hline
% \end{tabular}
